### 2015-07-20 conclusion.tex
Change name of tex file to 'spack-paper-sc15'
Name change spack-paper-sc15 -> spack-sc15
Build environment figure text.

The complexity of managing HPC software is rapidly increasing, and it
will continue unabated without better tools.
In this paper, we reviewed the state of software management tools 
across a number of HPC sites, with particular focus on Livermore
Computing (LC). While tools exist that can handle multi-configuration
installs, none of them addresses the combinatorial nature
of the software configuration space directly. None of them allows
a user to rapidly {\it compose} new parametric builds.

We introduced Spack, a package manager in development at LLNL, that
provides truly {\it parameterized} builds.  Spack implements
a novel, recursive {\it spec} syntax that simplifies the process of working
with large software configuration spaces, and it builds software 
so that it will run correctly, regardless of the environment.
We outlined a number of Spack's unique features, including
versioned virtual dependencies, and the {\it concretization} process,
which converts an underspecified build DAG into a buildable spec.

We showed through three use cases that Spack is already
increasing operational efficiency 
in production at LLNL.  We believe that the software management
techniques implemented in
Spack are applicable to a broad range of HPC facilities.
Spack is available online at: http://bit.ly/spack-git.

>>>>

The complexity of managing HPC software is rapidly increasing, and it
will continue unabated without better tools.
In this paper, we reviewed the state of software management tools
across a number of HPC sites, with particular focus on Livermore
Computing (LC). While tools exist that can handle multi-configuration
installs, none of them addresses the combinatorial nature
of the software configuration space directly. None of them allows
a user to rapidly {\it compose} new builds with version, compiler,
and dependency parameters.

We introduced Spack, a package manager in development at LLNL, that
provides truly {\it parameterized} builds.  Spack implements
a novel, recursive {\it spec} syntax that simplifies the process of working
with large software configuration spaces, and it builds software
so that it will run correctly, regardless of the environment.
We outlined a number of Spack's unique features, including
versioned virtual dependencies, and its novel {\it concretization}
process, which converts an abstract build DAG into a concrete,
buildable spec.

We showed through four use cases that Spack is already increasing
operational efficiency in production at LLNL.  We believe that the
software management techniques implemented in Spack are applicable
to a broad range of HPC facilities.
Spack is available online at http://github.com/scalability-llnl/spack.

### 2015-07-20 implementation-environment.tex
Build environment figure text.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figs/wrappers/wrapper-overhead.pdf}
	\caption{
		Build times with and without compiler wrappers\newline
		(\% overhead above bars).
		\label{fig:wrapper-overhead}
	}
\end{figure}

Argument parsing and indirection cause Spack's compiler wrappers to incur a small
but noticeable performance overhead.  Figure~\ref{fig:wrapper-overhead} shows build times
with and without the wrappers for seven different packages. Above each set of bars,
the percent overhead is written. The {\tt dyninst} and {\tt lapack} packages
use CMake to build, while the rest of the packages use autotools.
The relative overheads range from negligible (-0.4\%) in the case of {\tt dyninst},
and they are more exaggerated for shorter builds like {\tt mpileaks}, which
incurs 12.3\%.

### 2015-07-20 introduction.tex
Name change spack-paper-sc15 -> spack-sc15
Build environment figure text.

In this paper, we describe our experiences with the {\it Spack} package manager,
which we have developed at LLNL to manage increasing software complexity.
Specifically, this paper offers the following contributions:
\begin{enumerate}
\item A novel, recursive syntax for concisely specifying and querying
      the large parameter space of HPC packages;
\item A build methodology that ensures packages find their dependencies
      regardless of users' environments;
\item Spack: An implementation of these concepts; and
\item Three use cases that detail LLNL's use of Spack to compose
      software configurations rapidly, to manage Python installations, and
      to implement site-specific build policies.
\end{enumerate}

>>>>

In this paper, we describe our experiences with the {\it Spack} package manager,
which we have developed at LLNL to manage increasing software complexity.
Specifically, this paper offers the following contributions:
\begin{enumerate}
\item A novel, recursive syntax for concisely specifying and querying
      the large parameter space of HPC packages;
\item A build methodology that ensures packages find their dependencies
      regardless of users' environments;
\item Spack: An implementation of these concepts; and
\item Four use cases that detail LLNL's use of Spack to comcpose
      software configurations rapidly, to manage Python installations, and
      to implement site build policies, and to build an LLNL production code.
\end{enumerate}
